Visual Inference Test of the Hexagon Tile Map for Spatial Distributions

### 2019-12-19 survey/survey.Rmd
draft design

---
title: Visual Inference Test of the Hexagon Tile Map for Spatial Distributions
affiliation:
  author-columnar: true         ## one column per author
  #institution-columnar: true  ## one column per institution (multiple autors eventually)
  # wide: true                  ## one column wide author/affiliation fields

  institution:
    - name: Queensland University of Technology
      department: Science and Engineering Faculty
      location: Brisbane, Australia
      email: stephanie.kobakian@qut.edu.au
      mark: 1
      author:
        - name: Stephanie Kobakian
    - name: Monash University
      department: Econometrics and Business Statistics Faculty
      location: Melbourne, Australia
      email: dicook@monash.edu
      mark: 1
      author:
        - name: Dianne Cook
keywords: ["statistics", "visual inference", "geospatial", "population"]
abstract: |
  The abstract goes here.
  On multiple lines eventually.

bibliography: mybibfile.bib
output: rticles::ieee_article
---

Introduction
=============
<!-- no \IEEEPARstart -->
<!-- You must have at least 2 lines in the paragraph with the drop letter -->
<!-- (should never be an issue) -->
Geo-spatial statistics are often presented on the geographic map base. To present geo-spatial population statistics, information for individuals within each geographic region are often aggregated. A choropleth map is the common display to present aggreagated statistics for subdivisions of the geography, and they are often used to present statistics regarding the population. 
This visualisation method involves drawing the administrative boundaries and filling them with colour to communicate the value of the statistic. 
In Australia, there are sets of administrative boundaries that define subdivisions of the population at various granularities.

When presenting population statistics on a geographic map base, the size of the regions can allow errornous conclusions to be drawn about the state of the statistic over the entire population.
This occurs as large regions filled with a consistent colour or pettern can draw the attention of map readers, and small regions are not paid equal attention. XXX

@@

The Australian Cancer Atlas explores the burden of cancer on Australian communities. There are many cancer types presented, and can be explored on an individual or aggregate level. 
The Australian communities examined are Statistical Areas at Level 2 (SA2) used by the Australian Bureau of Statistics.
Bayesian spatial smoothing has been applied to incorporate the statistics of neighbouring areas, for both privacy and stability of the estimates.
The statistics that can be mapped are the diagnoses (Standardised Incidence Rates) and excess deaths for each SA2, communicated as the difference from the Australian average of the statistics.
The values of the statistic for each are communicated using a diverging colour scheme. Dark blue represents areas with values much less than the Australian average, and represents areas much greater than the Australian average.

@@

Map creators have the ability to present spatial statistics in alternative displays that can highlight the population.
This work aims to show that a hexagon tile map display is a viable alternative to the geographic map base for presenting population statistics.
The same data will be shown on a choropleth map, and on a hexagon tile map.
Comparing the results of participants who see the choropleth to those who see a hexagon tile map will show that population related distributions are spotted more frequently in a hexagon tile map display.

Methodology
============

@@

Experimental Design:
Three trends were tested, in each of the two displays.
For each of the

Line up protocol:

- Experimental design

  - The overall structure and operation of the experiment or observational experience.
  - The subject populations: The groups studied in the research including the size of each group and any features of the subjects which may be relevant to the topic being researched. 
  - The  variables that were changed between groups and the variables measured as a result of the changes.
  - The conditions under which the research was undertaken and any factors or variations in conditions which may have an impact on the results.
  - The methods of data analysis used in order to analyse and collate the results. 
  - Any limitations of the data collected

@@

@@

Here are two sample references: @Feynman1963118 [@Dirac1953888].

@@

<!-- \begin{figure}[!t] -->
<!-- \centering -->
<!-- \includegraphics[width=2.5in]{myfigure} -->
<!-- where an .eps filename suffix will be assumed under latex,  -->
<!-- and a .pdf suffix will be assumed for pdflatex; or what has been declared -->
<!-- via \DeclareGraphicsExtensions. -->
<!-- \caption{Simulation results for the network.} -->
<!-- \label{fig_sim} -->
<!-- \end{figure} -->

>>>>

---
title: "Which is Better: a Choropleth Map or Hexagon Tile Map? A comparison using visual inference with crowdsourcing?"
affiliation:
  author-columnar: true         ## one column per author
  #institution-columnar: true  ## one column per institution (multiple autors eventually)
  # wide: true                  ## one column wide author/affiliation fields
  institution:
    - name: Queensland University of Technology
      department: Science and Engineering Faculty
      location: Brisbane, Australia
      email: stephanie.kobakian@qut.edu.au
      mark: 1
      author:
        - name: Stephanie Kobakian
    - name: Monash University
      department: Econometrics and Business Statistics Faculty
      location: Melbourne, Australia
      email: dicook@monash.edu
      mark: 1
      author:
        - name: Dianne Cook
keywords: ["statistics", "visual inference", "geospatial", "population"]
abstract: |
  The abstract goes here.
  On multiple lines eventually.
dev: png
bibliography: mybibfile.bib
output: rticles::ieee_article
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  error = FALSE, 
  message = FALSE)
```

Introduction
=============
<!-- no \IEEEPARstart -->
<!-- You must have at least 2 lines in the paragraph with the drop letter -->
<!-- (should never be an issue) -->
Geo-spatial statistics are often presented on the geographic map base. To present geo-spatial population statistics, information for individuals within each geographic region are often aggregated. A choropleth map is the common display to present aggreagated statistics for geographic units, and they are often used to present statistics regarding the population. 
This visualisation method involves drawing the administrative boundaries and filling them with colour to communicate the value of the statistic. 
In Australia, there are many sets of administrative boundaries that define subdivisions of the population at various granularities.

When presenting population statistics on a geographic map base, the size of the regions can allow errornous conclusions to be drawn about the state of the statistic over the entire population.
This occurs as large regions filled with a consistent colour or pettern can draw the attention of map readers, and small regions are not paid equal attention.

@@

The Australian Cancer Atlas explores the burden of cancer on Australian communities. There are many cancer types presented, and they can be explored on an individual or aggregate level. 
The Australian communities examined are Statistical Areas at Level 2 (SA2)[@abs2016] used by the Australian Bureau of Statistics.
Bayesian spatial smoothing has been applied to incorporate the statistics of neighbouring areas, for both privacy and stability of the estimates.
The statistics that can be mapped are the diagnoses (Standardised Incidence Rates) and excess deaths for each SA2, communicated as the difference from the Australian average of the statistics.
The values of the statistic for each are communicated using a diverging colour scheme. Dark blue represents areas with values much less than the Australian average, and represents areas much greater than the Australian average.

@@

Map creators have the ability to present spatial statistics in alternative displays that can highlight the population.
This work aims to show that a hexagon tile map display is a viable alternative to the geographic map base for presenting population statistics.
The same data were shown on a choropleth map, and on a hexagon tile map.
Comparing the results of participants who see the choropleth to those who see a hexagon tile map will show that population related distributions are spotted more frequently in a hexagon tile map display.

Study Design
============

## Aims

This study aims to answer several questions around the presentation of spatial distributions:

1. Are spatial disease trends, that impact highly populated small areas, detected with higher accuracy when viewed in a hexagon tile map display?

2. Are people faster in detecting spatial disease trends, that impact highly populated small areas, when
using a hexagon tile map display?
3. Do people find hexagon tile maps more difficult to read than choropleth maps?
4. Are the reasons for choosing a plot different depending on the type of display?
5. Does an Australian resident find the choropleth map easier to read than the hexagon tile map?

## Methodology

@@

The online crowdsource platform Figure-Eight was used to recruit participants. 
A line up protocol was implemented to arrange 12 maps in each display. 
Individual displays were created by a combination of plot type, and spatial trend model.

The researchers contrasted the different plot designs, as hexagon tilemap
and geography in the lineups were created using the same data, and same null positions within the lineup.

The researchers compared the length of time taken, and the accuracy of the participants choices.

## The participants

There were 95 participants in the study. 
We recruited participants using the Figure-Eight crowd source platform by advertising this survey to participants that fulfilled the following crtieria:

• level 2 or level 3 on the Figure-Eight Platform.
• at least 18 years old

Participants then selected our task from the list of tasks available to them.

## The variables being manipulated and measured?

The variables that were changed between groups were the type of plot shown and the trend model.

Each participant was randomly allocated to either group A or group B when they begun the survey. This resulted in 42 participants allocated to group A, and 53 participants allocated to group B.

The levels of the factors measured in the experiment were:
• Plot type: *Geography, Hexagons*
• Trend: *Locations in two population centres, Locations in multiple population centres, South-East to North-West*

Factor combinations examined by each participant amount to 6 (2x3) lineup displays.
A participant did see the same data for both plot types. Four simulated sets of data were generated for each treatment.
This will generate 24 lineups (12 were geographic maps, and 12 were hexagon tile maps). Participants will evaluate 12 lineups, 6 of each plot type. Appendix A shows the experimental design visually.
For each of the six geographic displays and six hexagon displays, two of each trend model were shown to participants.

The variables measured as a result of the changes were the probability of detection each display and the time taken to submit responses.
To measure the accuracy of the detections, the plot chosen for each lineup evaluated was compared to the position of the real spatial trend plot in the lineup. A correct result occurs when the chosen plot matches the position of the real plot, this was recorded in an additional binary variable; 1 = correct; 0 = incorrect.
High efficiency occurs when a small amount of time is taken to evaluate each lineup. This will be measured as the numeric variable measuring the length of time taken to submit the answers to the evaluation of each line up.

## Participant training
Each participant saw three test displays orienting them to the task. Participants proceeded to the survey, this involved evaluating 12 displays.

## Experiment procudure and data collection
The participant submitted demographic questions and provided consent before evaluating the lineups.

Demographics were collected regarding the study participants:
• Gender (female / male / other),
• Degree education level achieved (high school / bachelors / masters / doctorate / other),
• Age range (18-24 / 25-34 / 35-44 / 45-54 / 55+ / other)
• Lived at least for one year in Australia (Yes / No )

Participants then moved to the evaulation phase.
The set of images differed for group A and group B.
After being allocated each individual was shown the 12 displays in randomised order.

Three questions were asked regarding each display:
- Plot choice
- Reason
- Difficulty

After completing the 12 evaluations, the participants were asked to submit their responses.

Data was collected through a web application containing the online survey.
Each participant used the internet to access the survey.

The data collection took place using a secure link between the survey web application and the googlesheet used to store results. The application would first connect to the googlesheet using the googlesheets [@sheets] R package, and interacted again at the completion of the survey by adding the participant's responses to the 12 displays as 12 rows of data in the googlesheet.

## The methods of data analysis used
The data analysis methods used in order to analyse and collate the results included downloading the survey submissions and opening them into the analysis software R [@RCore].

For each of the 12 lineup displays the researchers calculated:
• accuracy: the proportion of subjects who detected the data plot
• efficiency: average time taken to respond

### Visualisations
Side-by-side dot plots were made of accuracy (efficiency) against plot type, facetted by trend model type.

Similar plots were made of the feedback and demographic variables - reason for choice, reported difficulty, gender, age, education, having lived in Australia - against the design variables.

Plots will be made in R (R Core Team 2019), with the ggplot2 package (Wickham 2016).

### Modeling

The results will be analysed using a generalised linear model, with a subject random effect. There will be two main effects: plot type and trend model, which gives the fixed effects part of the model to be

$$\widehat{y_{ij}} = \mu + \tau_i + \delta_j + (\tau\delta)_{ij}, ~~~ i=1,2; ~j=1,2,3$$

where $y_{ij} = 0, 1$ whether the subject detected the data plot, $\mu$ is the overall mean, $\tau_i, i=1,2$ is the plot type effect, $\delta_j$ is the trend model effect. We are allowing for an interaction between plot type and trend model. Because the response is binary, a logistic model is used.

A similar model will be constructed for the efficiency, using a log time, and normal errors.

The feedback and demographic variables will possibly be incorporated as covariates.

Computation will be done using R [@RCore], with the `lme4` package [@lme4].

## Limitations of the data collection

This required internet connection for participants to access the survey

Ethics approval for the online survey was granted by QUT’s Ethics Committee (Ethics Application Number: 1900000991). All applicants provided informed consent in line with QUT regulations prior to participating in this research.

@@

```{r data}
###############################################################################

# Load Libraries
library(tidyverse)
library(lubridate)
library(broom)
library(readxl)
library(lme4)
library(ggthemes)

invthm <- theme(
  panel.background = element_rect(fill = "transparent", colour = NA), 
  plot.background = element_rect(fill = "transparent", colour = NA),
  legend.background = element_rect(fill = "transparent", colour = NA),
  legend.key = element_rect(fill = "transparent", colour = NA),
  text = element_text(colour = "white", size = 20),
  axis.text = element_text(colour = "white", size = 20)
)

# Downloaded data
d <- read_xlsx("../experiment-export.xlsx", sheet=2) %>%
  filter(!is.na(contributor)) %>%
  mutate(contributor = factor(contributor))
```

```{r}
###############################################################################
# Check data set 
# d %>% count(contributor, sort=TRUE)
# Need to clean multiple entries, 48, 24
# remove duplicated entries due to submit button
d <- d %>% group_by(group, contributor, image_name) %>%
  slice(1) %>% ungroup() %>% 
  arrange(group, contributor, plot_order)

# Now remove contributors who did not provide answers to most questions
keep <- d %>% count(contributor, sort = TRUE) %>% filter(n > 10)
d <- d %>% 
  filter(contributor %in% keep$contributor) %>%
  filter(contributor != "1234567890")

n_contributors <- d %>% count(contributor, sort=TRUE) %>% summarise(n_contributors = length(contributor))
```
The survey responses from participants were kept only if the participant submitted answers for all 12 displays. This resulted in `r n_contributors` surveyed.

```{r}
###############################################################################
# Augment
# add data replication number
#d %>% count(image_name) %>% print(n=24)
# image code <--> rep
replicate <- tibble(image_name = c("aus_cities_12_geo.png", "aus_cities_12_hex.png", 
                                   "aus_cities_3_geo.png", "aus_cities_3_hex.png",
                                   "aus_cities_4_geo.png", "aus_cities_4_hex.png",
                                   "aus_cities_9_geo.png", "aus_cities_9_hex.png",
                                   "aus_nwse_2_geo.png", "aus_nwse_2_hex.png",
                                   "aus_nwse_3_geo.png", "aus_nwse_3_hex.png",
                                   "aus_nwse_5_geo.png", "aus_nwse_5_hex.png",
                                   "aus_nwse_6_geo.png", "aus_nwse_6_hex.png",
                                   "aus_three_12_geo.png", "aus_three_12_hex.png",
                                   "aus_three_5_geo.png", "aus_three_5_hex.png",
                                   "aus_three_8_geo.png", "aus_three_8_hex.png",
                                   "aus_three_9_geo.png", "aus_three_9_hex.png"),
                    replicate = c(1, 1, 2, 2, 3, 3, 4, 4, 
                                  1, 1, 2, 2, 3, 3, 4, 4,
                                  1, 1, 2, 2, 3, 3, 4, 4))
# Add rep info to data
d <- d %>% left_join(., replicate, by = "image_name")
#d %>% count(group, image_name, sort=TRUE)`

###############################################################################
# Tidy for analysis
d <- d %>% 
  separate(image_name, c("nothing", "trend", "location", "type"), remove=FALSE) %>%
  select(-nothing) %>%
  mutate(location = as.numeric(location), 
    # detect measures the accuracy of the choice
         detect = ifelse(location == choice, 1, 0)) %>% 
  mutate(trend = case_when(
    trend == "cities" ~ "all cities",
    trend == "three" ~ "three cities",
    trend == "nwse" ~ "NW-SE")) %>% 
  mutate(trend = fct_relevel(trend, "NW-SE","three cities","all cities")) %>% 
  mutate(type = case_when(
    type == "hex" ~"Hexagons",
    TRUE~"Geography"
  ))

plots <- d %>% group_by(group, trend, type, location) %>%
  # pdetect measures the aggregated accuracy of the choices
  summarise(pdetect = length(detect[detect == 1])/length(detect))

plots %>% ggplot(aes(x = group, y = pdetect)) + 
  geom_boxplot() + 
  geom_jitter(width = 0.1) +
  ylim(c(0,1))

```

```{r}
# Check contributor performance
contribs <- d %>% group_by(group, contributor) %>%
  # pdetect measures the aggregated accuracy of the choices
  summarise(pdetect = length(detect[detect == 1])/length(detect))

# contribs %>% count(group)
# contribs %>% arrange(pdetect)

```

```{r}
# Plot performance
contribs %>% ggplot(aes(x = group, y = pdetect, label = contributor)) + 
  geom_boxplot() + 
  geom_jitter(width = 0.1) +
  ylim(c(0,1))
```

```{r}

# Create one record for each contributor, to examine demographics
dem_contribs <- d %>%
  group_by(contributor) %>%
  slice(1) %>% ungroup()

```

```{r}

###############################################################################
# Demographics of contributors
dem_contribs %>% count(gender)
dem_contribs %>% count(age)
dem_contribs %>% count(education)
dem_contribs %>% count(australia)

```

```{r}

###############################################################################
# Detectability rate for each lineup (image)
d_smry <- d %>% group_by(trend, type, location, replicate) %>%
  # pdetect measures the aggregated accuracy of the choices
  summarise(pdetect = length(detect[detect == 1])/length(detect)) %>%
  ungroup()

# Plot summary
ggplot(d_smry, aes(x=type, y=pdetect, colour = trend)) +
  geom_point(size = 3) +  
  geom_line(size = 1, aes(group = replicate)) +  
  facet_wrap(~trend) +  
  scale_colour_brewer(palette = "Paired") +
  xlab("Type of areas visualised") +
  ylab("Detection rate") + 
  ylim(0,1) + #invthm + 
  guides(colour = FALSE)

```
11 of the 12 real distribution plots were found more often in the hexagon display.
This was better than expected. As even geographic distributions were spotted in the hexagon lineup.

```{r}
##ggsave(filename = "figures/pilot/replicate_change.png", plot = repl_plot, device = "png", dpi = 300, width = 12, height = 8, units = "in", bg = "transparent")
##ggsave(filename = "figures/pilot/replicate_change.png", plot = repl_plot, device = "png", dpi = 300, width = 12, height = 8, units = "in")

# Numerical summary
diffs <- d_smry %>% spread(type, pdetect) %>%
  mutate(dif = Hexagons - Geography)
# Need to do the t-tests for these

ggplot(diffs) + 
  geom_point(aes(Geography, Hexagons, colour = trend)) +
  geom_abline(slope = 1) +
  xlim(0,1) + ylim(0,1) + coord_equal()

# Probability of detection using map types
test_dt <- t.test(pdetect ~ type, data = d_smry, alternative = "less")

test_dt$p.value

```

```{r}

d_time <- d %>% 
  group_by(trend, type, location, replicate) %>%
  summarise(m = mean(time_taken), s = sd(time_taken))
#d_time %>% print(n=24)

ggplot(d, aes(x=time_taken, fill = trend)) +
  geom_density(alpha = 0.4)

# Visual summary
ggplot(d_time, aes(x=type, y=m, colour = trend)) +
  geom_point(size = 3) +  
  geom_line(size = 1, aes(group = replicate)) +  
  facet_wrap(~trend) +  
  scale_colour_brewer(palette = "Paired") +
  xlab("Type of areas visualised") +
  ylab("Average time taken") + 
  guides(colour = FALSE)

#ggsave(filename = "figures/pilot/replicate_change_time.png", plot = repl_plot_t, device = "png", dpi = 300, width = 12, height = 8, units = "in", bg = "transparent")
##ggsave(filename = "figures/pilot/replicate_change.png", plot = repl_plot, device = "png", dpi = 300, width = 12, height = 8, units = "in")

```

```{r}

###########################################################
# Need to check certainty next

ggplot(d, aes(x = trend, y = certainty)) +
  geom_violin(draw_quantiles = c(0.25, 0.5, 0.75))
# certainty wasn't affected by the trend

ggplot(d %>% mutate(detect = as_factor(detect)), aes(x = detect, y = certainty)) +
  geom_violin(draw_quantiles = c(0.25, 0.5, 0.75))
# certainty was slightly higher for correct detections

```

```{r}
###########################################################
# Qualitative analysis of reason
d <- d %>% 
  mutate(reason = ifelse(reason =="0.0", "no reason", reason))

ggplot(d) + geom_bar(aes(x = reason)) +  
  facet_grid(trend ~ detect) +  
  scale_colour_brewer(palette = "Paired") +
  xlab("Type of areas visualised") + 
  guides(colour = FALSE) + coord_flip()

```

@@

@@

<!-- \begin{figure}[!t] -->
<!-- \centering -->
<!-- \includegraphics[width=2.5in]{myfigure} -->
<!-- where an .eps filename suffix were assumed under latex,  -->
<!-- and a .pdf suffix were assumed for pdflatex; or what has been declared -->
<!-- via \DeclareGraphicsExtensions. -->
<!-- \caption{Simulation results for the network.} -->
<!-- \label{fig_sim} -->
<!-- \end{figure} -->

### 2019-12-19 survey/survey.tex
draft design

@@

Geo-spatial statistics are often presented on the geographic map base.
To present geo-spatial population statistics, information for
individuals within each geographic region are often aggregated. A
choropleth map is the common display to present aggreagated statistics
for subdivisions of the geography, and they are often used to present
statistics regarding the population. This visualisation method involves
drawing the administrative boundaries and filling them with colour to
communicate the value of the statistic. In Australia, there are sets of
administrative boundaries that define subdivisions of the population at
various granularities.

When presenting population statistics on a geographic map base, the size
of the regions can allow errornous conclusions to be drawn about the
state of the statistic over the entire population. This occurs as large
regions filled with a consistent colour or pettern can draw the
attention of map readers, and small regions are not paid equal
attention. XXX

@@

The Australian Cancer Atlas explores the burden of cancer on Australian
communities. There are many cancer types presented, and can be explored
on an individual or aggregate level. The Australian communities examined
are Statistical Areas at Level 2 (SA2) used by the Australian Bureau of
Statistics. Bayesian spatial smoothing has been applied to incorporate
the statistics of neighbouring areas, for both privacy and stability of
the estimates. The statistics that can be mapped are the diagnoses
(Standardised Incidence Rates) and excess deaths for each SA2,
communicated as the difference from the Australian average of the
statistics. The values of the statistic for each are communicated using
a diverging colour scheme. Dark blue represents areas with values much
less than the Australian average, and represents areas much greater than
the Australian average.

@@

Map creators have the ability to present spatial statistics in
alternative displays that can highlight the population. This work aims
to show that a hexagon tile map display is a viable alternative to the
geographic map base for presenting population statistics. The same data
will be shown on a choropleth map, and on a hexagon tile map. Comparing
the results of participants who see the choropleth to those who see a
hexagon tile map will show that population related distributions are
spotted more frequently in a hexagon tile map display.

\hypertarget{methodology}{%
\section{Methodology}\label{methodology}}

@@

Experimental Design: Three trends were tested, in each of the two
displays. For each of the

Line up protocol:

\begin{itemize}
\item
  Experimental design

  \begin{itemize}
  \tightlist
  \item
    The overall structure and operation of the experiment or
    observational experience.
  \item
    The subject populations: The groups studied in the research
    including the size of each group and any features of the subjects
    which may be relevant to the topic being researched.
  \item
    The variables that were changed between groups and the variables
    measured as a result of the changes.
  \item
    The conditions under which the research was undertaken and any
    factors or variations in conditions which may have an impact on the
    results.
  \item
    The methods of data analysis used in order to analyse and collate
    the results.
  \item
    Any limitations of the data collected
  \end{itemize}
\end{itemize}

@@

@@

\hypertarget{modeling}{%
\subsection{Modeling}\label{modeling}}

@@

Here are two sample references: ({\textbf{???}}; {\textbf{???}}).

@@

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-SIEDAMD}{}%
Buja, Andreas, Dianne Cook, Heike Hofmann, Michael Lawrence, Eun-Kyung
Lee, Deborah F. Swayne, and Hadley Wlckham. 2009. ``Statistical
Inference for Exploratory Data Analysis and Model Diagnostics.''
\emph{Philosophical Transactions: Mathematical, Physical and Engineering
Sciences} 367 (1906): 4361--83.
\url{http://www.jstor.org/stable/40485732}.

>>>>

\usepackage{graphicx}
% We will generate all images so they have a width \maxwidth. This means
% that they will get their normal width if they fit onto the page, but
% are scaled down if they would overflow the margins.
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth
\else\Gin@nat@width\fi}
\makeatother
\let\Oldincludegraphics\includegraphics
\renewcommand{\includegraphics}[1]{\Oldincludegraphics[width=\maxwidth]{#1}}

@@

Geo-spatial statistics are often presented on the geographic map base.
To present geo-spatial population statistics, information for
individuals within each geographic region are often aggregated. A
choropleth map is the common display to present aggreagated statistics
for geographic units, and they are often used to present statistics
regarding the population. This visualisation method involves drawing the
administrative boundaries and filling them with colour to communicate
the value of the statistic. In Australia, there are many sets of
administrative boundaries that define subdivisions of the population at
various granularities.

When presenting population statistics on a geographic map base, the size
of the regions can allow errornous conclusions to be drawn about the
state of the statistic over the entire population. This occurs as large
regions filled with a consistent colour or pettern can draw the
attention of map readers, and small regions are not paid equal
attention.

@@

The Australian Cancer Atlas explores the burden of cancer on Australian
communities. There are many cancer types presented, and they can be
explored on an individual or aggregate level. The Australian communities
examined are Statistical Areas at Level 2 (SA2)(``Australian Statistical
Geography Standard (ASGS)'' 2018) used by the Australian Bureau of
Statistics. Bayesian spatial smoothing has been applied to incorporate
the statistics of neighbouring areas, for both privacy and stability of
the estimates. The statistics that can be mapped are the diagnoses
(Standardised Incidence Rates) and excess deaths for each SA2,
communicated as the difference from the Australian average of the
statistics. The values of the statistic for each are communicated using
a diverging colour scheme. Dark blue represents areas with values much
less than the Australian average, and represents areas much greater than
the Australian average.

@@

Map creators have the ability to present spatial statistics in
alternative displays that can highlight the population. This work aims
to show that a hexagon tile map display is a viable alternative to the
geographic map base for presenting population statistics. The same data
were shown on a choropleth map, and on a hexagon tile map. Comparing the
results of participants who see the choropleth to those who see a
hexagon tile map will show that population related distributions are
spotted more frequently in a hexagon tile map display.

\hypertarget{study-design}{%
\section{Study Design}\label{study-design}}

\hypertarget{aims}{%
\subsection{Aims}\label{aims}}

This study aims to answer several questions around the presentation of
spatial distributions:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  Are spatial disease trends, that impact highly populated small areas,
  detected with higher accuracy when viewed in a hexagon tile map
  display?
\item
  Are people faster in detecting spatial disease trends, that impact
  highly populated small areas, when using a hexagon tile map display?
\item
  Do people find hexagon tile maps more difficult to read than
  choropleth maps?
\item
  Are the reasons for choosing a plot different depending on the type of
  display?
\item
  Does an Australian resident find the choropleth map easier to read
  than the hexagon tile map?
\end{enumerate}

\hypertarget{methodology}{%
\subsection{Methodology}\label{methodology}}

@@

The online crowdsource platform Figure-Eight was used to recruit
participants. A line up protocol was implemented to arrange 12 maps in
each display. Individual displays were created by a combination of plot
type, and spatial trend model.

The researchers contrasted the different plot designs, as hexagon
tilemap and geography in the lineups were created using the same data,
and same null positions within the lineup.

The researchers compared the length of time taken, and the accuracy of
the participants choices.

\hypertarget{the-participants}{%
\subsection{The participants}\label{the-participants}}

There were 95 participants in the study. We recruited participants using
the Figure-Eight crowd source platform by advertising this survey to
participants that fulfilled the following crtieria:

• level 2 or level 3 on the Figure-Eight Platform. • at least 18 years
old

Participants then selected our task from the list of tasks available to
them.

\hypertarget{the-variables-being-manipulated-and-measured}{%
\subsection{The variables being manipulated and
measured?}\label{the-variables-being-manipulated-and-measured}}

The variables that were changed between groups were the type of plot
shown and the trend model.

Each participant was randomly allocated to either group A or group B
when they begun the survey. This resulted in 42 participants allocated
to group A, and 53 participants allocated to group B.

The levels of the factors measured in the experiment were: • Plot type:
\emph{Geography, Hexagons} • Trend: \emph{Locations in two population
centres, Locations in multiple population centres, South-East to
North-West}

Factor combinations examined by each participant amount to 6 (2x3)
lineup displays. A participant did see the same data for both plot
types. Four simulated sets of data were generated for each treatment.
This will generate 24 lineups (12 were geographic maps, and 12 were
hexagon tile maps). Participants will evaluate 12 lineups, 6 of each
plot type. Appendix A shows the experimental design visually. For each
of the six geographic displays and six hexagon displays, two of each
trend model were shown to participants.

The variables measured as a result of the changes were the probability
of detection each display and the time taken to submit responses. To
measure the accuracy of the detections, the plot chosen for each lineup
evaluated was compared to the position of the real spatial trend plot in
the lineup. A correct result occurs when the chosen plot matches the
position of the real plot, this was recorded in an additional binary
variable; 1 = correct; 0 = incorrect. High efficiency occurs when a
small amount of time is taken to evaluate each lineup. This will be
measured as the numeric variable measuring the length of time taken to
submit the answers to the evaluation of each line up.

\hypertarget{participant-training}{%
\subsection{Participant training}\label{participant-training}}

Each participant saw three test displays orienting them to the task.
Participants proceeded to the survey, this involved evaluating 12
displays.

\hypertarget{experiment-procudure-and-data-collection}{%
\subsection{Experiment procudure and data
collection}\label{experiment-procudure-and-data-collection}}

The participant submitted demographic questions and provided consent
before evaluating the lineups.

Demographics were collected regarding the study participants: • Gender
(female / male / other), • Degree education level achieved (high school
/ bachelors / masters / doctorate / other), • Age range (18-24 / 25-34 /
35-44 / 45-54 / 55+ / other) • Lived at least for one year in Australia
(Yes / No )

Participants then moved to the evaulation phase. The set of images
differed for group A and group B. After being allocated each individual
was shown the 12 displays in randomised order.

Three questions were asked regarding each display: - Plot choice -
Reason - Difficulty

After completing the 12 evaluations, the participants were asked to
submit their responses.

Data was collected through a web application containing the online
survey. Each participant used the internet to access the survey.

The data collection took place using a secure link between the survey
web application and the googlesheet used to store results. The
application would first connect to the googlesheet using the
googlesheets (Bryan and Zhao 2018) R package, and interacted again at
the completion of the survey by adding the participant's responses to
the 12 displays as 12 rows of data in the googlesheet.

\hypertarget{the-methods-of-data-analysis-used}{%
\subsection{The methods of data analysis
used}\label{the-methods-of-data-analysis-used}}

The data analysis methods used in order to analyse and collate the
results included downloading the survey submissions and opening them
into the analysis software R ({\textbf{???}}).

For each of the 12 lineup displays the researchers calculated: •
accuracy: the proportion of subjects who detected the data plot •
efficiency: average time taken to respond

\hypertarget{visualisations}{%
\subsubsection{Visualisations}\label{visualisations}}

Side-by-side dot plots were made of accuracy (efficiency) against plot
type, facetted by trend model type.

Similar plots were made of the feedback and demographic variables -
reason for choice, reported difficulty, gender, age, education, having
lived in Australia - against the design variables.

Plots will be made in R (R Core Team 2019), with the ggplot2 package
(Wickham 2016).

\hypertarget{modeling}{%
\subsubsection{Modeling}\label{modeling}}

The results will be analysed using a generalised linear model, with a
subject random effect. There will be two main effects: plot type and
trend model, which gives the fixed effects part of the model to be

\[\widehat{y_{ij}} = \mu + \tau_i + \delta_j + (\tau\delta)_{ij}, ~~~ i=1,2; ~j=1,2,3\]

where \(y_{ij} = 0, 1\) whether the subject detected the data plot,
\(\mu\) is the overall mean, \(\tau_i, i=1,2\) is the plot type effect,
\(\delta_j\) is the trend model effect. We are allowing for an
interaction between plot type and trend model. Because the response is
binary, a logistic model is used.

A similar model will be constructed for the efficiency, using a log
time, and normal errors.

The feedback and demographic variables will possibly be incorporated as
covariates.

Computation will be done using R ({\textbf{???}}), with the
\texttt{lme4} package ({\textbf{???}}).

\hypertarget{limitations-of-the-data-collection}{%
\subsection{Limitations of the data
collection}\label{limitations-of-the-data-collection}}

This required internet connection for participants to access the survey

Ethics approval for the online survey was granted by QUT's Ethics
Committee (Ethics Application Number: 1900000991). All applicants
provided informed consent in line with QUT regulations prior to
participating in this research.

@@

The survey responses from participants were kept only if the participant
submitted answers for all 12 displays. This resulted in 95 surveyed.

\includegraphics{survey_files/figure-latex/unnamed-chunk-2-1.pdf}

\includegraphics{survey_files/figure-latex/unnamed-chunk-4-1.pdf}

\begin{verbatim}
## # A tibble: 2 x 2
##   gender     n
##   <chr>  <int>
## 1 He        70
## 2 She       25
\end{verbatim}

\begin{verbatim}
## # A tibble: 6 x 2
##   age         n
##   <chr>   <int>
## 1 18 - 24    15
## 2 25 - 34    37
## 3 35 - 44    23
## 4 45 - 54    11
## 5 55+         6
## 6 NA          3
\end{verbatim}

\begin{verbatim}
## # A tibble: 3 x 2
##   education       n
##   <chr>       <int>
## 1 Bach           56
## 2 High School    25
## 3 Masters        14
\end{verbatim}

\begin{verbatim}
## # A tibble: 2 x 2
##   australia     n
##   <chr>     <int>
## 1 No           93
## 2 Yes           2
\end{verbatim}

\includegraphics{survey_files/figure-latex/unnamed-chunk-7-1.pdf} 11 of
the 12 real distribution plots were found more often in the hexagon
display. This was better than expected. As even geographic distributions
were spotted in the hexagon lineup.

\includegraphics{survey_files/figure-latex/unnamed-chunk-8-1.pdf}

\begin{verbatim}
## [1] 0.004079185
\end{verbatim}

\includegraphics{survey_files/figure-latex/unnamed-chunk-9-1.pdf}
\includegraphics{survey_files/figure-latex/unnamed-chunk-9-2.pdf}

\includegraphics{survey_files/figure-latex/unnamed-chunk-10-1.pdf}
\includegraphics{survey_files/figure-latex/unnamed-chunk-10-2.pdf}

\includegraphics{survey_files/figure-latex/unnamed-chunk-11-1.pdf}

@@

\hypertarget{modeling-1}{%
\subsection{Modeling}\label{modeling-1}}

@@

@@

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-abs2016}{}%
``Australian Statistical Geography Standard (ASGS).'' 2018.
\emph{Australian Bureau of Statistics}. Australian Government.
\href{\%7Bhttps://www.abs.gov.au/websitedbs/D3310114.nsf/home/Australian\%20\%20\%20Statistical\%20Geography\%20Standard\%20(ASGS)\%7D}{\{https://www.abs.gov.au/websitedbs/D3310114.nsf/home/Australian   Statistical Geography Standard (ASGS)\}}.

\leavevmode\hypertarget{ref-sheets}{}%
Bryan, Jennifer, and Joanna Zhao. 2018. \emph{Googlesheets: Manage
Google Spreadsheets from R}.
\url{https://CRAN.R-project.org/package=googlesheets}.

\leavevmode\hypertarget{ref-SIEDAMD}{}%
Buja, Andreas, Dianne Cook, Heike Hofmann, Michael Lawrence, Eun-Kyung
Lee, Deborah F. Swayne, and Hadley Wlckham. 2009. ``Statistical
Inference for Exploratory Data Analysis and Model Diagnostics.''
\emph{Philosophical Transactions: Mathematical, Physical and Engineering
Sciences} 367 (1906): 4361--83.
\url{http://www.jstor.org/stable/40485732}.
